The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-06-25 paper/ms.tex
Fix couple typos suggested by ref

We now repeat the same procedure as in Figure~\ref{fig:one_orbit_wrong_ref}
but for systematic offsets between $0$ and $500\,\pc$ in the $z$ and $x$
components. In Figure~\ref{fig:many_orbit_wrong_ref}, we report $\Delta
J_i/J_i$ for the three different fiducial orbits in Table~\ref{tab:orbits}.
The upper panels of Figure~\ref{fig:many_orbit_wrong_ref} shows the spread
induced in each action for an offset in the $z$-component. In the lower panels
we consider offsets in the $x$ component (i.e. the solar radius). The left,
center, and right columns show the fractional spread in the values computed
for $J_z$, $J_{\phi}$, and $J_R$, respectively.

@@

The upper right panel of Figure~\ref{fig:many_orbit_wrong_ref} shows that the
fractional error in $J_z$ is more exaggerated for more planar (disk-like)
orbits. For \thin{}, a systematic offset of $15\,\pc$ in the $z$-coordinate
results in a $25\%$ deviation in $J_z$, while a $120\,\pc$ offset results in
the same deviation for \thick{}. We find that \halo{} is relatively resistant
to errors in the midplane, with only $\sim15\%$ error in $J_z$ out to an
offset of $500\,\pc$.

>>>>

We now repeat the same procedure as in Figure~\ref{fig:one_orbit_wrong_ref}
but for systematic offsets between $0$ and $500\,\pc$ in the $z$ and $x$
components. In Figure~\ref{fig:many_orbit_wrong_ref}, we report $\Delta
J_i/J_i$ for the three different fiducial orbits in Table~\ref{tab:orbits}.
The upper panels of Figure~\ref{fig:many_orbit_wrong_ref} shows the spread
induced in each action for an offset in the $z$-component. In the lower panels
we consider offsets in the $x$ component (i.e. the solar radius). \textbf{The left,
center, and right columns show the fractional spread in the values computed
for $J_R$, $J_{\phi}$, and $J_z$, respectively.}

@@

The upper right panel of Figure~\ref{fig:many_orbit_wrong_ref} shows that the
fractional error in $J_z$ is more exaggerated for more planar (disk-like)
orbits. For \thin{}, a systematic offset of $15\,\pc$ in the $z$-coordinate
results in a $25\%$ deviation in $J_z$, while a $120\,\pc$ offset results in
the same deviation for \thick{}. We find that \halo{} is relatively
\textbf{insensitive} to errors in the midplane, with only $\sim15\%$ error in
$J_z$ out to an offset of $500\,\pc$.
